


```{r getData, eval=FALSE}
link='https://github.com/EvansDataScience/VisualAnalytics_2_tabularData/raw/master/data/eduwa.rda'

#getting the data TABLE from the file in the cloud:
load(file=url(link))
```




```{r ggplot1, eval=FALSE}

tableFreq=as.data.frame(ToPlot)
names(tableFreq)=c("locale","pct")
#you have:
tableFreq
```


* Call the library:

```{r ggplot_call, warning=FALSE}
library(ggplot2)
```

* Create the base _object_, which is not a plot, just informing the main variables:

```{r ggplot_base, eval=FALSE}
#base GGPLOT2 starts with a "base", telling WHAT VARIABLES TO PLOT
tableFreq$locale <- factor(tableFreq$locale, levels = tableFreq$locale[order(tableFreq$pct)])

base= ggplot(data = tableFreq, 
             aes(x = locale,
                 y = pct))

```

* On top of the previous object, add the layer that produces the main plots (the next layers will add or customize elements in the plot):

```{r bar_gg, eval=FALSE}
plot1 = base + geom_bar(fill ="yellow",
                        stat = 'identity') # y is just what it is!
plot1
```

* We can now pay attention to the titles:

```{r title_gg, eval=FALSE}
plot2 = plot1 + labs(title=titleText2,
                     x =NULL, 
                     y = NULL,
                     caption = sourceText)
plot2

```

* Add the reference lines:

```{r refl_gg, eval=FALSE}
plot3 = plot2 + geom_hline(yintercept = 25, 
                           linetype="dotted", 
                           size=1.5, 
                           alpha=0.5)
plot3
```

* Customize the axes:

```{r units_gg, eval=FALSE}
library(scales)

# customize Y axis
plot4 = plot3 + scale_y_continuous(breaks=c(0,10, 25,40,50),
                                 limits = c(0, 50), # expand = c(0, 0),
                                 labels=scales::unit_format(suffix = '%')) 
plot4
```

* Less ink and title/subtitle positions:
```{r title2_gg, eval=FALSE}
plot5 = plot4 + theme(panel.background = element_rect(fill = "white",
                                                    colour = "yellow"),
                    plot.caption = element_text(hjust = 0), 
                    plot.title = element_text(hjust = 0.5))
plot5
```

* annotating the bars:

```{r annot_gg, eval=FALSE}
plot6 = plot5 + geom_text(aes(y = pct ,
                            label = paste0(round(pct,2), '%')),
                        vjust=1, # if flipping 'hjust'
                        size = 3)

plot6 + coord_flip()

```

